Waveform and Passive Beamforming Design for Intelligent Reflecting Surface-Aided Wireless Information and Power Transfer

### 2020-09-16 main.tex
:pencil: Path loss vs distance

\begin{section}{System Model}
	As shown in Figure \ref{fi:system}, we consider an IRS-aided SWIPT system where a $M$-antenna transmitter delivers information and power simultaneously, through a $L$-reflector IRS, to a single-antenna user over $N$ orthogonal subbands. Suppose a total bandwidth $B$ with evenly-spaced subbands centered at frequency $f_n$ ($n=1,\dots,N$). Perfect Channel State Information (CSI) with negligible training overhead is assumed to explore the analytical upper-bound of the proposed design. A quasi-static block fading channel model is considered for all links, and we focus on one particular block where the channels are approximately unchanged. Two practical co-located receiver architectures are compared in terms of R-E region. Specifically, TS divides each time slot into orthogonal data and energy slots and performs a time sharing between WPT and Wireless Information Transfer (WIT). In comparison, PS splits the received signal into individual ID and EH streams such that the splitting ratio $\rho$ is coupled with waveform and IRS design. Perfect synchronization is assumed among the three parties in both scenarios, and signals reflected by IRS for two and more times are omitted.

@@

\begin{section}{Performance Evaluations}
	\begin{figure}
		\centering
		\def\svgwidth{\columnwidth}
		\import{assets/}{layout.pdf_tex}
		\caption{System layout}
		\label{fi:layout}
	\end{figure}
	To evaluate the performance of the proposed IRS-aided SWIPT system, we characterize and compare the average R-E regions under typical setups. Consider a large open space WiFi-like environment at a center frequency of 5.18 \si{\GHz} with reference bandwidth $B=1$ \si{\MHz}. As shown in Figure \ref{fi:layout}, we assume the IRS moves along a horizontal line parallel to the AP-user path. Define the projection of the AP-IRS path onto the AP-user path as $d_H$ and let the distance from the IRS to the AP-user path be $d_V$. Denote $d_D$, $d_I$, $d_R$ as the length of direct, incident, reflective paths. We fix $d_D=15$ \si{\meter}, $d_V=2$ \si{\meter} and choose a reference $d_H=2$ \si{\meter}. For all channels, the path loss and fading parameters are obtained from IEEE TGn channel model D \cite{Erceg2004}. Reference path loss is set to $L_0=-35$ \si{\dB} at $d_0=1$ \si{\meter}, and taps are modelled as i.i.d. random variables with normalized total power. We choose number of subbands $N=16$ as reference and assume no spatial correlation across all arrays. Rectenna parameters are taken as $k_2=0.0034$, $k_4=0.3829$, $R_{\text{ant}}=50$ \si{\ohm}. The average Effective Isotropic Radiated Power (EIRP) is fixed to $-36$ \si{\dBi} while the reference average noise power is $\sigma_n=-40$ \si{\dBm} at all subbands. We also assume 0 \si{\dBi} IRS element gain and 2 \si{\dBi} receive antenna gain. For the algorithm, the tolerance is $\epsilon=10^{-8}$, the number of candidates in the Gaussian randomization method is $Q=10^{3}$, and the R-E region is averaged over 200 channel realizations. In the R-E boundary, the leftmost point corresponds to WPT ($\rho=1$) where power can be allocated simultaneously to modulated and unmodulated waveform to maximize the average output DC current. On the other hand, the rightmost point corresponds to WIT ($\rho=0$) where the solution coincides with water-filling algorithm allocating all power to modulated waveform only. For a fair comparison, the $x$-axis of the plots has been normalized to per-subband rate.

@@

	Figure \ref{fi:re_subband} illustrates the average R-E region versus the number of subband $N$. \textit{First}, it is observed that increasing $N$ reduces the per-subband rate but boosts the harvested energy. The reason is that although each subband receives a smaller proportion of the total power, more balanced terms are introduced to further amplify the output DC current, as demonstrated by the scaling laws in \cite{Clerckx2018b}. The result also confirmed that from the perspective of WPT, dedicated multisine waveform is unnecessary for a small $N$ but is required for a large $N$. As shown in \ref{eq:y_I4} and \ref{eq:y_P4}, the only difference of modulated and unmodulated waveform on $z$ exists in the fourth-order terms, where $\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^4(t)\right\}\right\}$ has $N^2$ monomials with a modulation gain of 2 and $\mathcal{A}\left\{y_{P}^4(t)\right\}$ has $(2N^3+N)/3$ monomials without modulation gain. Therefore, superposed waveform enlarges the R-E region for a sufficiently large $N$ (typically no smaller than 4). However, an excessively large $N$ not only requires high computation complexity but also operates out of the small-signal harvester model, thus become prohibitive. \textit{Second}, the R-E region is convex for $N = 2, 4$ and concave-convex for $N = 8, 16$. This has the consequence that PS outperforms TS for a small $N$ and is outperformed for a large $N$. When $N$ is in between, the optimal strategy is a combination of both, i.e. a time sharing between the WPT point and the tangent WIPT point obtained by power splitting. Compared with the linear harvester model that requires no dedicated power waveform and always prefer PS, the rectifier nonlinearity enlarges the R-E region by favouring a different waveform and transmission strategy, both heavily depends on $N$.
\end{section}

>>>>

\begin{section}{System Model}
	As shown in Fig. \ref{fi:system}, we consider an IRS-aided SWIPT system where a $M$-antenna transmitter delivers information and power simultaneously, through a $L$-reflector IRS, to a single-antenna user over $N$ orthogonal subbands. Suppose a total bandwidth $B$ with evenly-spaced subbands centered at frequency $f_n$ ($n=1,\dots,N$). Perfect Channel State Information (CSI) with negligible training overhead is assumed to explore the analytical upper-bound of the proposed design. A quasi-static block fading channel model is considered for all links, and we focus on one particular block where the channels are approximately unchanged. Two practical co-located receiver architectures are compared in terms of R-E region. Specifically, TS divides each time slot into orthogonal data and energy slots and performs a time sharing between WPT and Wireless Information Transfer (WIT). In comparison, PS splits the received signal into individual ID and EH streams such that the splitting ratio $\rho$ is coupled with waveform and IRS design. Perfect synchronization is assumed among the three parties in both scenarios, and signals reflected by IRS for two and more times are omitted.

@@

\begin{section}{Performance Evaluations}
	\begin{figure}
		\centering
		\def\svgwidth{\columnwidth}
		\import{assets/}{layout.pdf_tex}
		\caption{System layout}
		\label{fi:layout}
	\end{figure}
	To evaluate the performance of the proposed IRS-aided SWIPT system, we characterize and compare the average R-E regions under typical setups. Consider a large open space WiFi-like environment at a center frequency of 5.18 \si{\GHz} with reference bandwidth $B=1$ \si{\MHz}. As shown in Fig. \ref{fi:layout}, we assume the IRS moves along a horizontal line parallel to the AP-user path. Define the projection of the AP-IRS path onto the AP-user path as $d_H$ and let the distance from the IRS to the AP-user path be $d_V$. Denote $d_D$, $d_I$, $d_R$ as the length of direct, incident, reflective paths, such that $d_I=\sqrt{d_H^2+d_V^2}$, $d_R=\sqrt{(d_D-d_H)^2+d_V^2}$. We fix $d_D=15$ \si{\meter}, $d_V=2$ \si{\meter} and choose a reference $d_H=2$ \si{\meter}. For all channels, the path loss and fading parameters are obtained from IEEE TGn channel model D \cite{Erceg2004}, and we regard all channels as NLoS unless otherwise mentioned. Reference path loss is set to $L_0=-35$ \si{\dB} at $d_0=1$ \si{\meter}, and taps are modelled as i.i.d. random variables with normalized total power. We choose number of subbands $N=16$ as reference and assume no spatial correlation across all arrays. Rectenna parameters are taken as $k_2=0.0034$, $k_4=0.3829$, $R_{\text{ant}}=50$ \si{\ohm}. The average Effective Isotropic Radiated Power (EIRP) is fixed to $-36$ \si{\dBi} while the reference average noise power is $\sigma_n=-40$ \si{\dBm} at all subbands. We also assume 0 \si{\dBi} IRS element gain and 2 \si{\dBi} receive antenna gain. For the algorithm, the tolerance is $\epsilon=10^{-8}$, the number of candidates in the Gaussian randomization method is $Q=10^{3}$, and the R-E region is averaged over 200 channel realizations. In the R-E boundary, the leftmost point corresponds to WPT ($\rho=1$) where power can be allocated simultaneously to modulated and unmodulated waveform to maximize the average output DC current. On the other hand, the rightmost point corresponds to WIT ($\rho=0$) where the solution coincides with water-filling algorithm allocating all power to modulated waveform only. For a fair comparison, the $x$-axis of the plots has been normalized to per-subband rate.

@@

	Fig. \ref{fi:re_subband} illustrates the average R-E region versus the number of subband $N$. \textit{First}, it is observed that increasing $N$ reduces the per-subband rate but boosts the harvested energy. The reason is that although each subband receives a smaller proportion of the total power, more balanced terms are introduced to further amplify the output DC current, as demonstrated by the scaling laws in \cite{Clerckx2018b}. Waveform amplitude in Fig. \ref{fi:waveform_subband} also confirmed that from the perspective of WPT, dedicated multisine waveform is unnecessary for a small $N$ but is required for a large $N$. As shown in \ref{eq:y_I4} and \ref{eq:y_P4}, the only difference of modulated and unmodulated waveform on $z$ exists in the fourth-order terms, where $\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^4(t)\right\}\right\}$ has $N^2$ monomials with a modulation gain of 2 and $\mathcal{A}\left\{y_{P}^4(t)\right\}$ has $(2N^3+N)/3$ monomials without modulation gain. Therefore, superposed waveform enlarges the R-E region for a sufficiently large $N$ (typically no smaller than 4). However, an excessively large $N$ not only requires high computation complexity but also operates out of the small-signal harvester model, thus become prohibitive. \textit{Second}, the R-E region is convex for $N = 2, 4$ and concave-convex for $N = 8, 16$. This has the consequence that PS outperforms TS for a small $N$ and is outperformed for a large $N$. When $N$ is in between, the optimal strategy is a combination of both, i.e. a time sharing between the WPT point and the tangent WIPT point obtained by power splitting. Compared with the linear harvester model that requires no dedicated power waveform and always prefer PS, the rectifier nonlinearity enlarges the R-E region by favouring a different waveform and transmission strategy, both heavily depends on $N$.

	\begin{figure}
		\centering
		\begin{adjustbox}{width=\linewidth}
			\input{assets/re_distance.tex}
		\end{adjustbox}
		\caption{Average R-E region versus AP-IRS horizontal distance}
		\label{fi:re_distance}
	\end{figure}

	\begin{figure}
		\centering
		\begin{adjustbox}{width=\linewidth}
			\input{assets/path_loss.tex}
		\end{adjustbox}
		\caption{Path loss versus distance}
		\label{fi:path_loss}
	\end{figure}

	In Fig. \ref{fi:re_distance}, we compare the average R-E region achieved by different AP-IRS horizontal distance $d_H$. A \textit{first} observation is that placing the IRS closer to either the AP or the user would improve the R-E tradeoff. This origins from the exponential path loss model, where the signal attenuation increases fast at a short range and experiences marginal effect when transmission distance is long. As shown in Fig. \ref{fi:path_loss}, although the piecewise TGn path loss model further penalizes large $d$ (greater than 10 \si{\meter} for model D), it is still beneficial to have a short-long or long-short transmission setup. On the other hand, the result suggests that developing an IRS near the AP can effectively extend the operation range of SWIPT systems. Considering the passive characteristic of IRS, opportunities are that it can be directly controlled and powered by the SWIPT network.

	\begin{figure}
		\centering
		\begin{adjustbox}{width=\linewidth}
			\input{assets/re_reflector.tex}
		\end{adjustbox}
		\caption{Average R-E region versus the number of reflectors}
		\label{fi:re_reflector}
	\end{figure}

	The impact of number of reflectors $L$ on the average R-E region is revealed in Fig. \ref{fi:re_reflector}.
\end{section}
